### 2014-11-08 contract-language.tex
Added Delta axioms

\noindent The $\Delta$ referred in the above defintion is a conjunction of
assumptions about the nature of primitive relations, e.g., $\Rvis$ and $\Rso$
are irreflexive, and the happens-before relation $\hbZ$ is acyclic. A
\emph{well-formed} axiomatic execution ($\E$) is expected to satisfy these
assumptions (i.e., $\E \models \Delta$).

If the contract ($\cv_{op}$) of an operation ($\mathit{op}$) is \emph{weaker
than} a store contract ($\cv_{st}$), then constraints expressed by the former
are implied by guarantees provided by the latter. The completeness of
first-order logic allows us to assert that any well-formed execution ($\E$)
that satisfies $\cv_{st}$ (i.e., $\E\models \cv_{st}$) also satisfies
$\cv_{op}$ (i.e., $\E \models \cv_{op}$). Consequently, it is safe to execute
operation $\mathit{op}$ under a store consistency level captured by $\cv_{st}$.

@@

\begin{proof}
  Hypothesis:
  \begin{smathpar}
  \begin{array}{cr}
    \auxred{} {\E,\langle op,\tau \rangle;\sigma \pll \Sigma} {\eff}
    {\E', \sigma \pll \Sigma} & H\npp\\
    \E' \models \cv_\tau[\eff/\cureff] & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\tau$ is the contract class of $\cv$, by inversion, we have
  $\cv \le \cv_\tau$. By the definition of $\le$ relation:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \forall \cureff.\,\cv_\tau \Rightarrow \cv & H\npp\\
  \end{array}
  \end{smathpar}
   Since $\eff$ denotes new effect, it is a fresh variable that does
   not occur free in $\Delta$. From $H2$, after instantiating bound
   $\cureff$ with $\eff$, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \cv_\tau[\eff/\cureff] \Rightarrow \cv[\eff/\cureff]
      & H\npp\\
  \end{array}
  \end{smathpar}
  Due to the soundness of natural deduction for first-order logic,
  $H3$ implies that for all models $\mathcal{M}$ such that
  $\mathcal{M} \models \Delta$, if $\mathcal{M} \models
  \cv_\tau[\eff/\cureff]$ then $\mathcal{M} \models
  \cv[\eff/\cureff]$. Since $\E'$ is well-formed, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \E' \models \Delta & H\npp\\
  \end{array}
  \end{smathpar}
  Proof follows from $H1$ and $H4$.
  \qed
\end{proof}

>>>>

\noindent The $\Delta$ referred in the above definition is a conjunction of
following assumptions about the nature of primitive relations:

\begin{itemize}
\item $\visZ$ relates actions on the same object:
  \begin{itemize}
    \item $\forall a,b. \visZ(a,b) \Rightarrow \sameobjZ(a,b)$
  \end{itemize}
\item $\soZ$ is a transitive relation:
  \begin{itemize}
    \item $\forall a,b,c. \soZ(a,b) \conj \soZ(b,c) \Rightarrow \soZ(a,c)$
  \end{itemize}
\item $\sameobjZ$ is an equivalence relation:
  \begin{itemize}
    \item $\forall a. \sameobjZ(a,a)$
    \item $\forall a,b. \sameobjZ(a,b) \Rightarrow \sameobjZ(b,a)$
    \item $\forall a,b,c. \soZ(a,b) \conj \soZ(b,c) \Rightarrow \soZ(a,c)$
  \end{itemize}
\end{itemize}

\noindent A \emph{well-formed} axiomatic execution ($\E$) is expected
to satisfy these assumptions:

\begin{definition}
An axiomatic execution $\E$ is said to be well-formed if and only if
$\E \models \Delta$.
\end{definition}

\noindent If the contract ($\cv_{op}$) of an operation ($\mathit{op}$)
is \emph{weaker than} a store contract ($\cv_{st}$), then constraints
expressed by the former are implied by guarantees provided by the
latter. The completeness of first-order logic allows us to assert that
any well-formed execution ($\E$) that satisfies $\cv_{st}$ (i.e.,
$\E\models \cv_{st}$) also satisfies $\cv_{op}$ (i.e., $\E \models
\cv_{op}$). Consequently, it is safe to execute operation
$\mathit{op}$ under a store consistency level captured by $\cv_{st}$.

@@

\begin{proof}
  Hypothesis:
  \begin{smathpar}
  \begin{array}{cr}
    \auxred{} {\E,\langle op,\tau \rangle;\sigma \pll \Sigma} {\eff}
    {\E', \sigma \pll \Sigma} & H\npp\\
    \E' \models \cv_\tau[\eff/\cureff] & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\tau$ is the contract class of $\cv$, by inversion, we have
  $\cv \le \cv_\tau$. By the definition of $\le$ relation:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \cv_\tau \Rightarrow \cv & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\cureff$ occurs free in $\cv$ and $\cv_\tau$, but not in
  $\Delta$, we introduce quantifier to bind $\cureff$:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \forall \cureff.\,\cv_\tau \Rightarrow \cv & H\npp\\
  \end{array}
  \end{smathpar}
   Since $\eff$ denotes new effect, it is a fresh variable that does
   not occur free in $\Delta$. From $H3$, after instantiating bound
   $\cureff$ with $\eff$, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \Delta \vdash \cv_\tau[\eff/\cureff] \Rightarrow \cv[\eff/\cureff]
      & H\npp\\
  \end{array}
  \end{smathpar}
  Due to the soundness of natural deduction for first-order logic,
  $H4$ implies that for all models $\mathcal{M}$ such that
  $\mathcal{M} \models \Delta$, if $\mathcal{M} \models
  \cv_\tau[\eff/\cureff]$ then $\mathcal{M} \models
  \cv[\eff/\cureff]$. Since $\E'$ is well-formed, we have:
  \begin{smathpar}
  \begin{array}{cr}
    \E' \models \Delta & H\npp\\
  \end{array}
  \end{smathpar}
  Proof follows from $H1$, $H5$, and $H4$.
  \qed
\end{proof}
